Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-14 paper/paper.tex
Added figures to the appendix.
Still need to put them in line with the text instead of on the next page.

\documentclass[letter,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[toc,page]{appendix}
\usepackage{amsmath, amsthm, amssymb}

@@

The vector $\vec{p} - \vec{l}$ is along a generatrix of the cone, so it is perpendicular to $\vec{p} - \vec{c}$, which points from the center of the sphere to the point of tangency (figure [reference to "sphere shadow figure 1.png"]). Therefore, a right triangle is formed by $\vec{p}$, $\vec{c}$, and $\vec{l}$, with $\vec{c}$ and $\vec{l}$ at the ends of the hypotenuse. The length $L=\|\vec{c}-\vec{l}\|$ can be calculated from the givens and the distance $r=\|\vec{p}-\vec{c}\|$ is a given. By the pythagorean theorem the length of the other leg is $L'=\|\vec{p}-\vec{l}\|=\sqrt{L^2-r^2}$. In figure [reference to "sphere shadow figure 2.png"] the triangle formed by the projection and orthogonal projection of $\vec{p}-\vec{l}$ onto $\vec{c}-\vec{l}$ is shown with the triangle formed by $\vec{p}$, $\vec{c}$, and $\vec{l}$. The triangles are similar because they share two congruent angles. Thus their sides have the same proportions. In particular:
\[
k = {\|orth_{\vec{c}-\vec{l}} (\vec{p} - \vec{l})\|\over \|proj_{\vec{c}-\vec{l}} (\vec{p} - \vec{l})\|} = {r'\over L''} = {r\over L'} = {r\over\sqrt{L^2-r^2}}
\]
Now we use the defintions of $orth_{\vec{u}} \vec{v}$ and $proj_{\vec{u}} \vec{v}$ to simplify equation (\ref{xproperty}).
\begin{align*}
proj_{\vec{u}} \vec{v} = \vec{u} {\vec{u}\cdot\vec{v}\over \vec{u}\cdot\vec{u}}\\
orth_{\vec{u}} \vec{v} = \vec{v} - proj_{\vec{u}} \vec{v}
\end{align*}
Start by squaring both sides of \ref{xproperty} and substituting. Let $\vec{d} = \vec{c}-\vec{l}$, $y = \vec{x}-\vec{l}$.
\begin{align*}
\|\vec{y} - \vec{d} {\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}}\|^2 = \|\vec{d} {\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}}\|^2 \cdot k^2\\
\vec{y}\cdot\vec{y}-2\vec{y}\cdot\vec{d} {\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}}+\vec{d}\cdot\vec{d}({\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}})^2 = (\vec{d}\cdot\vec{d}) ({\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}})^2 \cdot k^2
\end{align*}
Multiply each side by $\vec{d}\cdot\vec{d}$:
\begin{align*}
(\vec{y}\cdot\vec{y})(\vec{d}\cdot\vec{d})-2(\vec{d}\cdot\vec{y})^2+(\vec{d}\cdot\vec{y})^2  = (\vec{d}\cdot\vec{y})^2 \cdot k^2\\
(\vec{y}\cdot\vec{y})(\vec{d}\cdot\vec{d})-(\vec{d}\cdot\vec{y})^2  = (\vec{d}\cdot\vec{y})^2 \cdot k^2
\end{align*}
Now we find the intersection of this cone with the $z=0$ plane.

>>>>

\documentclass[letter,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[toc,page]{appendix}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}

@@

The vector $\vec{p} - \vec{l}$ is along a generatrix of the cone, so it is perpendicular to $\vec{p} - \vec{c}$, which points from the center of the sphere to the point of tangency (see figure \ref{fig:shadow_1}). Therefore, a right triangle is formed by $\vec{p}$, $\vec{c}$, and $\vec{l}$, with $\vec{c}$ and $\vec{l}$ at the ends of the hypotenuse. The length $L=\|\vec{c}-\vec{l}\|$ can be calculated from the givens and the distance $r=\|\vec{p}-\vec{c}\|$ is a given. By the pythagorean theorem the length of the other leg is $L'=\|\vec{p}-\vec{l}\|=\sqrt{L^2-r^2}$. In figure \ref{fig:shadow_2} the triangle formed by the projection and orthogonal projection of $\vec{p}-\vec{l}$ onto $\vec{c}-\vec{l}$ is shown with the triangle formed by $\vec{p}$, $\vec{c}$, and $\vec{l}$. The triangles are similar because they share two congruent angles. Thus their sides have the same proportions. In particular:
\[
k = {\|orth_{\vec{c}-\vec{l}} (\vec{p} - \vec{l})\|\over \|proj_{\vec{c}-\vec{l}} (\vec{p} - \vec{l})\|} = {r'\over L''} = {r\over L'} = {r\over\sqrt{L^2-r^2}}
\]

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{sphere_shadow_figure_1.png}
    \caption{Awesome Image}
    \label{fig:shadow_1}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{sphere_shadow_figure_2.png}
    \caption{Awesome Image}
    \label{fig:shadow_2}
\end{figure}

%\includegraphics[scale=0.60]{sphere_shadow_figure_2}

Now we use the defintions of $orth_{\vec{u}} \vec{v}$ and $proj_{\vec{u}} \vec{v}$ to simplify equation (\ref{xproperty}).
\begin{align*}
proj_{\vec{u}} \vec{v} = \vec{u} {\vec{u}\cdot\vec{v}\over \vec{u}\cdot\vec{u}}\\
orth_{\vec{u}} \vec{v} = \vec{v} - proj_{\vec{u}} \vec{v}
\end{align*}
Start by squaring both sides of \ref{xproperty} and substituting. Let $\vec{d} = \vec{c}-\vec{l}$, $y = \vec{x}-\vec{l}$.
\begin{align*}
\|\vec{y} - \vec{d} {\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}}\|^2 = \|\vec{d} {\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}}\|^2 \cdot k^2\\
\vec{y}\cdot\vec{y}-2\vec{y}\cdot\vec{d} {\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}}+\vec{d}\cdot\vec{d}({\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}})^2 = (\vec{d}\cdot\vec{d}) ({\vec{d}\cdot\vec{y}\over \vec{d}\cdot\vec{d}})^2 \cdot k^2
\end{align*}
Multiply each side by $\vec{d}\cdot\vec{d}$:
\begin{align*}
(\vec{y}\cdot\vec{y})(\vec{d}\cdot\vec{d})-2(\vec{d}\cdot\vec{y})^2+(\vec{d}\cdot\vec{y})^2  = (\vec{d}\cdot\vec{y})^2 \cdot k^2\\
(\vec{y}\cdot\vec{y})(\vec{d}\cdot\vec{d})-(\vec{d}\cdot\vec{y})^2  = (\vec{d}\cdot\vec{y})^2 \cdot k^2
\end{align*}
Now we find the intersection of this cone with the $z=0$ plane.
